Supplementary materials

### 2022-09-25 RR_manuscript/supplementary_materials.Rmd
fix machine learning typo

<!-- Begin Table --> 
```{r}
#| label: descriptives-table
#| results: 'asis'
bind_rows(
  tbl_team_desc %>% 
    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`), 
  tbl_categorical_desc %>% 
    select(desc = Metric, Metric = Type, val1 = n, val2 = perc) %>% 
    mutate(val1 = glue::glue("{val1}")), 
  tbl_model_desc %>% 
    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`)
) %>% 
  mutate(order = c(
    1, 6, 4, 3, 5, 2, 
    25, 24, 26, 28, 27, 29, 
    30, 8, 7, 10, 9, 11, 
    12, 18, 17, 15, 14, 
    16, 13, 19, 
    20, 22, 21, 23, 
    31, 32, 33, 34, 35
    )
  ) %>% 
  arrange(order) %>% 
  select(-order) %>% 
  mutate(desc = str_replace_all(desc, "team_desc", " "), 
    desc = str_replace_all(desc, "model_desc", "N"), 
    desc = case_when(
      Metric != "Models" & desc == "N" ~ " ", 
      Metric != "Frequentist" & desc == "Framework" ~ " ", 
      Metric != "Linear model" & desc == "Model" ~ " ", 
      Metric != "F0" & desc == "Outcome" ~ " ", 
      Metric != "Word" & desc == "Temporal window" ~ " ", 
      Metric != "Categorical" & desc == "Typicality operationalization" ~ " ", 
      TRUE ~ desc)
    ) %>% 
  filter(Metric != "n. random smooths") %>% 
  mutate(Metric = str_remove_all(Metric, "n. "), 
         Metric = str_to_sentence(Metric)) %>% 
  rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 
    `\\bf{Mean (SD)}` = val2) %>% 
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 7) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Acoustic analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 8) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ",  .before = 15) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 22) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 28) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Statistical analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 29) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ",
    `\\bf{Mean (SD)}` = " ", .before = 33) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 38) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", 
    `\\bf{Range}` = "\\bf{Range}", `\\bf{Mean (SD)}` = "\\bf{Mean (SD)}", 
    .before = 39) %>% 
  kbl(., booktabs = T, align = c("l", "l", "r", "r"), escape = F, 
    longtable = F, linesep = "", 
    caption = glue::glue("Descriptive statistics of all contributing teams and their acoustic and statistical analyses. The summary includes data from {pull_from_tib(team_desc_df, stage, 'Submitted', n_teams)} teams and  {pull_from_tib(team_desc_df, stage, 'Submitted', n_analysts)} analysts."), 
    label = "descriptives-table") %>%
  kable_styling(full_width = F, latex_options = "scale_down") %>% 
  add_indent(c(9, 16, 23, 30, 34, 40)) %>% 
  add_indent(43:44, all_cols = T) %>% 
  row_spec(8, hline_after = T) %>% 
  row_spec(29, hline_after = T)
```
<!-- END TABLE -->

>>>>

<!-- Begin Table --> 
```{r}
#| label: descriptives-table
#| results: 'asis'
bind_rows(
  tbl_team_desc %>% 
    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`), 
  tbl_categorical_desc %>% 
    select(desc = Metric, Metric = Type, val1 = n, val2 = perc) %>% 
    mutate(val1 = glue::glue("{val1}")), 
  tbl_model_desc %>% 
    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`)
) %>% 
  mutate(order = c(
    1, 6, 4, 3, 5, 2, 
    25, 24, 26, 28, 27, 29, 
    30, 8, 7, 10, 9, 11, 
    12, 18, 17, 15, 14, 
    16, 13, 19, 
    20, 22, 21, 23, 
    31, 32, 33, 34, 35
    )
  ) %>% 
  arrange(order) %>% 
  select(-order) %>% 
  mutate(desc = str_replace_all(desc, "team_desc", " "), 
    desc = str_replace_all(desc, "model_desc", "N"), 
    desc = case_when(
      Metric != "Models" & desc == "N" ~ " ", 
      Metric != "Frequentist" & desc == "Framework" ~ " ", 
      Metric != "Linear model" & desc == "Model" ~ " ", 
      Metric != "F0" & desc == "Outcome" ~ " ", 
      Metric != "Word" & desc == "Temporal window" ~ " ", 
      Metric != "Categorical" & desc == "Typicality operationalization" ~ " ", 
      TRUE ~ desc)
    ) %>% 
  filter(Metric != "n. random smooths") %>% 
  rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 
    `\\bf{Mean (SD)}` = val2) %>% 
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 7) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Acoustic analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 8) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ",  .before = 15) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 22) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 28) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Statistical analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 29) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ",
    `\\bf{Mean (SD)}` = " ", .before = 33) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 38) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", 
    `\\bf{Range}` = "\\bf{Range}", `\\bf{Mean (SD)}` = "\\bf{Mean (SD)}", 
    .before = 39) %>% 
  kbl(., booktabs = T, align = c("l", "l", "r", "r"), escape = F, 
    longtable = F, linesep = "", 
    caption = glue::glue("Descriptive statistics of all contributing teams and their acoustic and statistical analyses. The summary includes data from {pull_from_tib(team_desc_df, stage, 'Submitted', n_teams)} teams and  {pull_from_tib(team_desc_df, stage, 'Submitted', n_analysts)} analysts."), 
    label = "descriptives-table") %>%
  kable_styling(full_width = F, latex_options = "scale_down") %>% 
  add_indent(c(9, 16, 23, 30, 34, 40)) %>% 
  add_indent(43:44, all_cols = T) %>% 
  row_spec(8, hline_after = T) %>% 
  row_spec(29, hline_after = T)
```
<!-- END TABLE -->
